---
title: "Models"
format: html
execute: 
  echo: false
---

```{r}
#| message: false
#| warning: false
library(tidybayes)
library(tidyverse)
library(gtsummary)
library(brms)
```

```{r}
#| message: false
#| warning: false
poll_data <- tibble(biden = c(rep(1, 655), 
                              rep(0, 904)))

fit_bern <- brm(formula = biden ~ 1, data = poll_data, family = bernoulli(), refresh = 0, silent = 2, seed = 9)

ndata <- tibble(.rows = 1)
```

```{r}
#| label: plot
#| message: false
#| warning: false

fit_bern |>
  add_epred_draws(newdata = ndata) |>
  select(.epred) |>
  ggplot(aes(x = .epred)) + 
  geom_density(aes(y = after_stat(count/sum(count)))) +
  scale_x_continuous(labels = scales::percent_format()) +
  scale_y_continuous(labels = scales::percent_format()) +
  labs(title = "Posterior Distribution for p", subtitle = "There is a 95% chance for a value between XX and XX", y = "Probability", x = "Proportion, p, of Red Beads in Urn")
```

Using data from a YouGov poll of 1,559 US adult citizens, conducted March 10 - 12, 2024, we seek to understand what proportion of voters will support Biden in the 2024 election. Biden’s popularity might change significantly over the course of the election campaign. In the poll, Biden’s support was much less than 50%. We estimate that Biden’s percentage of the vote in Election Day will be about 42%, plus or minus 2.5%.

$$ biden_i =  \mu + \epsilon_i $$

